SoK: The Evolution of Web Application Attack Defenses

### 2014-10-22 docs/questioning.tex
adding more material especially for training methods

\author{
\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
Panos Louridas,\IEEEauthorrefmark{2},
Michalis Polychronakis,\IEEEauthorrefmark{1}
and Angelos Keromytis\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
Network Security Lab\\
Department of Computer Scinence\\
Columbia University\\
\{dimitro, angelos\}@cs.columbia.edu\\
\IEEEauthorrefmark{2}
Software Engineering and Security Lab\\
Department of Management Science and Technology\\
Athens University of Economics and Business\\
louridas@aueb.gr
}}

@@

% {\it tainting},
% {\it instruction set randomization} ({{\sc isr}}),
% {\it policy enforcement} and {\it training}.

>>>>

\author{
\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
Panos Louridas,\IEEEauthorrefmark{2},
Michalis Polychronakis,\IEEEauthorrefmark{1}
and Angelos Keromytis\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
Network Security Lab\\
Department of Computer Scinence\\
Columbia University\\
\{dimitro, mikepo, angelos\}@cs.columbia.edu\\
\IEEEauthorrefmark{2}
Software Engineering and Security Lab\\
Department of Management Science and Technology\\
Athens University of Economics and Business\\
louridas@aueb.gr
}}

@@

\subsubsection{Runtime Tainting}

Runtime tainting is based on data-flow analysis.
In practice, it enforces security policies by marking untrusted
(``tainted") data and tracing its flow through the program.
Since information flow in a system cannot be verified by examining
a single execution trace of the system, the results of taint
analysis will necessarily reflect approximate information regarding
the information flow characteristics of the system to which it is applied.

\subsubsection{Policy Enforcement}

In this method, developers must define
specific security policies on the server side.
Then the policies are enforced either in the user's
browser at runtime or in a server-side proxy that
intercepts server responses.

\subsubsection{Code Rewriting}

\subsubsection{Training}

Training techniques are based on the ideas of Denning's original
intrusion detection framework~\cite{Den87}.
In particular, a training mechanism,
registers all valid legitimate code statements
during a training phase, most of the time in the form of signatures.
This can be done in various ways according to the implementation.
Then, only those will be accepted, approved or recognized during
production.

Training methods that detect JavaScript-driven {\sc xss} attacks
generate and store valid JavaScript code in various
forms, and detect attacks as outliers from the set of valid code statements.
{\it {\sc swap}}~\cite{WPLKK09} encodes all the legitimate scripts that exist in the
original application. Then, a JavaScript detection component placed in a web proxy
searches for injected scripts in the server's responses. If no injected scripts
are found, the proxy decodes the legitimate scripts and sends them to the
client.
% dimitro: more mechanisms TBA.

In the case of {\sc dsl}-driven injection attacks
the various countermeasures follow a similar pattern.
An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
{\sc sql} injection attacks by recording all database transactions.
Subsequent refinements by Valeur et al.~\cite{VMV05}
tagged each transaction with the corresponding application
as an extension of their anomaly detection framework called
{\it libAnomaly}\footnote[6]{\url{http://seclab.cs.ucsb.edu/academic/projects/projects/libanomaly/}}.
Furthermore, {\sc amnesia}~\cite{HO05,HO06} is a tool that also detects {\sc sql}
injection attacks by associating a query model with the location of every
{\sc sql} statement within the application. Then at runtime,
monitors the application's execution to detect when {\sc sql} statements
diverge from the expected model.
{\it {\sc sd}river}~\cite{MS09,MKS09} is a signature-based
mechanism that prevents
{\sc sql} and {\sc xp}ath injection attacks against web applications. 
The signatures generated during a training phase,
are based on features that can depend either on the
code statement or on its execution environment (i.e. the stack trace).
Then, at runtime, the mechanism checks all statements for compliance
and can block code statements containing injected elements.
By associating a complete stack trace with the root of an {\sc sql} statement, 
the mechanism can correlate {\sc sql} statements with their call sites.  
This increases the specificity of the stored signatures and 
avoids false alarms. 
% dimitro: more mechanisms TBA.
